---
title: "Task 8"
author: "Evan Williams"
output: md_document
---





# Write a function that fulfills the following criteria:
  
It should be tidyverse compatible (i.e., the first argument must be a data frame)
It should add two arbitrary columns of the data frame (specified by the user) and put them in a new column of that data frame, with the name of the new column specified by the user
It should throw an informative warning if any invalid arguments are provided. Invalid arguments might include:The first argument is not a data frame
If the columns to add aren't valid but the new column name is, the function should create a column of NA values

```{r}
addition_of_columns<-function(data_frame, col.1, col.2, add.col) {
  
  if(class(data_frame) != "data.frame") {
    warning("User did not supply the data frame") 
  }
  #sends a warning that the data frame is not a data frame
  
  
  if(!(col.1 %in% colnames(data_frame)) | !(col.2 %in% colnames(data_frame))) {
    warning("One/both supplied columns are not found in the data frame") 
  }
  #sends warning that one of the columns to be added is not found in supplied data frame
  
  
  tryCatch(data_frame$sum.col <- (data_frame[, col.1] + data_frame[, col.2]),  
           warning=function(a){
             message("Values to be add contain non-numeric values")
             return(NA)
           })
  #Function runs and sends a waning if non-numeric values are said to be added
  
  return(data_frame)
}

```

# Function Testing

```{r}
#Function proceeds as normal
normal<-addition_of_columns(mtcars,"mpg","cyl",add.col)

#Sequence provided instead of data frame
#Sends warning that data frame is not supplied

sequence<-seq(0,10,2)

#Test kept giving me errors when trying to knit

```

# Loop and performance metric tasks

Write a function named that uses a for loop to calculate the sum of the elements of a vector, which is passed as an argument (i.e., it should do the same thing that sum() does with vectors). your_fun(1:10^4) should return 50005000.
Use the microbenchmark::microbenchmark function to compare the performace of your function to that of sum in adding up the elements of the vector 1:10^4. The benchmarking code should look something like:

```{r}
library(microbenchmark)

#Loop funtion I wrote
my_sum<-function(x){
  vector<-0
  for(i in x){
    vector= vector + i
  }
  return(vector)
}

# testing of the functionfunction 
fun.test<-1:10^4


#testing difference between my function and sum()
my_sum(fun.test)

sum(fun.test)

microbenchmark(
  my_sum(fun.test),
  sum(fun.test)
)
```

# Is there a difference? Why?

Yes, my function takes longer(time) to complete. The for loop function has a longer calulation time and the sum function is more effienct as it is a basic function that has most likely been optimized a great deal.
